BIOL424 Project Proposal

### 2021-08-21 proposal.tex
Add the statement of novelty to the project proposal.
Add the method outline to the project proposal.

@@

>>>>

As far as I am aware, my study will constitute the first attempt to select the optimal grouping, from among all possible groupings, of a competitive interaction matrix based on quality of model fit.

@@

Data will consist of the results of species interaction experiments, covering at least each monoculture and pairwise configuration of approximately 7--9 species.
It will be obtained from the studies examined by \textcite{kinlock2019meta}, or similar.

Every possible grouping will be tested using a brute force method.
Given $n$ species, this yields $B_n$ groupings of the rows and $B_n$ groupings of the columns, for $B_n^2$ groupings overall, where $B_n$ is the $n$th Bell number.
$B_9^2 = \num{447195609}$, indicating that $9$ species will be approximately the upper feasible limit for this analysis.

For each possible grouping, a Lotka--Volterra model, with intrinsic growth rates parameterised individually and competition coefficients parameterised according to the groupings, will be fitted to the model.
The AIC of each such model shall be taken as the result, and the AIC values of different models may be examined to test the different hypotheses listed above.
Particular attention will also be paid to the lowest AIC value of all configurations: the optimal model.
